### 2017-09-29 TF-vldb2018/sec-intro.tex

Another issue it that team formation is accompanied with a highly dynamic situation. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We illustrate this with an example.

@@

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
We also propose two optimization techniques: incrementally computing radius varied balls and density based filtering for speeding up computations.

>>>>

Another issue is that team formation is accompanied with a highly dynamic situation. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We illustrate this with an example.

@@

\stab (2) We develop a batch algorithm for computing top-$k$ teams via team simulation (Section~\ref{sec-tsimAlg}).
We study the satisfiability problem for pattern graphs, a new problem raised in the presence of capacity bounds for graph pattern matching .
We also propose two optimization techniques, incrementally computing radius varied balls and density based filtering, for speeding up computations.
